Case Study: 16S microbiome data (Schubert et al., 2014)

### 2018-04-23 datasets/microbiome/microbiome-baxter.Rmd
Remove nmids and change ashs to ashq

First, we'll create an object of `BenchDesign` class to hold the data and 
add the benchmark methods to the `BenchDesign` object. We'll do this for a few
values of nmids, to explore its effects on the outputs. We remove ASH from
the default comparison.

@@

```{r, baxter-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(otu_bench_file)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/crc_baxter_results.tar.gz"
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = otu_bench_file)
} else {
    sb <- readRDS(otu_bench_file)
}
```

@@

```{r, eval=FALSE}
assays(sb)[["qvalue"]][, "ashs"] %>% max()
sum(is.na(assays(sb)[["qvalue"]][, "scott-empirical"]))
sum(is.na(assays(sb)[["qvalue"]][, "lfdr"]))
```

@@

```{r, baxter-logubi-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(otu_bench_file_log_ubiquity)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/crc_baxter_results.tar.gz"
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = otu_bench_file_log_ubiquity)
} else {
    sb <- readRDS(otu_bench_file_log_ubiquity)
}
```

@@

First, we'll create an object of `BenchDesign` class to hold the data and 
add the benchmark methods to the `BenchDesign` object. We'll do this for a few
values of nmids, to explore its effects on the outputs. We remove ASH from
the comparison.

@@

```{r, baxter-genus-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/crc_baxter_results.tar.gz"
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = gns_bench_file)
} else {
    sb <- readRDS(gns_bench_file)
}
```

@@

```{r, baxter-genus-logubi-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file_log_ubiquity)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/crc_baxter_results.tar.gz"
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = gns_bench_file_log_ubiquity)
} else {
    sb <- readRDS(gns_bench_file_log_ubiquity)
}
```

>>>>

First, we'll create an object of `BenchDesign` class to hold the data and 
add the benchmark methods to the `BenchDesign` object. We remove ASH from
the default comparison.

@@

```{r, baxter-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(otu_bench_file)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/crc_baxter_results.tar.gz"
    saveRDS(sb, file = otu_bench_file)
} else {
    sb <- readRDS(otu_bench_file)
}
```

@@

```{r, eval=FALSE}
assays(sb)[["qvalue"]][, "ashq"] %>% max()
sum(is.na(assays(sb)[["qvalue"]][, "scott-empirical"]))
sum(is.na(assays(sb)[["qvalue"]][, "lfdr"]))
```

@@

```{r, baxter-logubi-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(otu_bench_file_log_ubiquity)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/crc_baxter_results.tar.gz"
    saveRDS(sb, file = otu_bench_file_log_ubiquity)
} else {
    sb <- readRDS(otu_bench_file_log_ubiquity)
}
```

@@

First, we'll create an object of `BenchDesign` class to hold the data and 
add the benchmark methods to the `BenchDesign` object. We remove ASH from
the comparison.

@@

```{r, baxter-genus-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/crc_baxter_results.tar.gz"
    saveRDS(sb, file = gns_bench_file)
} else {
    sb <- readRDS(gns_bench_file)
}
```

@@

```{r, baxter-genus-logubi-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file_log_ubiquity)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/crc_baxter_results.tar.gz"
    saveRDS(sb, file = gns_bench_file_log_ubiquity)
} else {
    sb <- readRDS(gns_bench_file_log_ubiquity)
}
```

### 2018-04-23 datasets/microbiome/microbiome-enigma.Rmd
Remove nmids and change ashs to ashq

```{r enigma-readdata}
## load OTU table and metadata
otu <- read.table(file.path(enigma_dir, "enigma.otu_table_resampled_updated_r.txt.gz"), 
                  sep='\t', header = TRUE, row.names = 1)
meta <- read.csv(file.path(enigma_dir, "enigma.metadata.txt"), sep='\t')

@@

```{r, ph-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(ph_bench_file)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = ph_bench_file)
} else {
    sb <- readRDS(ph_bench_file)
}
```

@@

```{r, so4-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(so4_bench_file)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = so4_bench_file)
} else {
    sb <- readRDS(so4_bench_file)
}
```

@@

```{r, al-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(al_bench_file)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = al_bench_file)
} else {
    sb <- readRDS(al_bench_file)
}
```

>>>>

```{r, enigma-readdata}
## load OTU table and metadata
print(file.path(enigma_dir, "enigma.otu_table_resampled_updated_r.txt.gz"))
otu <- read.table(file.path(enigma_dir, "enigma.otu_table_resampled_updated_r.txt.gz"), 
                  sep='\t', header = TRUE, row.names = 1)
meta <- read.csv(file.path(enigma_dir, "enigma.metadata.txt"), sep='\t')

@@

```{r, ph-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(ph_bench_file)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    saveRDS(sb, file = ph_bench_file)
} else {
    sb <- readRDS(ph_bench_file)
}
```

@@

```{r, so4-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(so4_bench_file)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    saveRDS(sb, file = so4_bench_file)
} else {
    sb <- readRDS(so4_bench_file)
}
```

@@

```{r, al-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(al_bench_file)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    saveRDS(sb, file = al_bench_file)
} else {
    sb <- readRDS(al_bench_file)
}
```

### 2018-04-23 datasets/microbiome/microbiome-goodrich.Rmd
Remove nmids and change ashs to ashq

```{r, goodrich-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(otu_bench_file)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ob_goodrich_results.tar.gz"
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = otu_bench_file)
} else {
    sb <- readRDS(otu_bench_file)
}
```

@@

First, we'll create an object of `BenchDesign` class to hold the data and 
add the benchmark methods to the `BenchDesign` object. We'll do this for a few
values of nmids, to explore its effects on the outputs.

@@

```{r, goodrich-genus-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ob_goodrich_results.tar.gz"
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = gns_bench_file)
} else {
    sb <- readRDS(gns_bench_file)
}
```

>>>>

```{r, goodrich-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(otu_bench_file)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ob_goodrich_results.tar.gz"
    saveRDS(sb, file = otu_bench_file)
} else {
    sb <- readRDS(otu_bench_file)
}
```

@@

First, we'll create an object of `BenchDesign` class to hold the data and 
add the benchmark methods to the `BenchDesign` object.

@@

```{r, goodrich-genus-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ob_goodrich_results.tar.gz"
    saveRDS(sb, file = gns_bench_file)
} else {
    sb <- readRDS(gns_bench_file)
}
```

### 2018-04-23 datasets/microbiome/microbiome-papa.Rmd
Remove nmids and change ashs to ashq

```{r, papa-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(otu_bench_file)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ibd_alm_results.tar.gz"
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = otu_bench_file)
} else {
    sb <- readRDS(otu_bench_file)
}
```

@@

```{r, papa-genus-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ibd_alm_results.tar.gz"
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = gns_bench_file)
} else {
    sb <- readRDS(gns_bench_file)
}
```

@@

```{r, papa-genus-logubi-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file_log_ubi)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ibd_alm_results.tar.gz"
    metadata(sb)$nmids <- nmids
    saveRDS(sb, file = gns_bench_file_log_ubi)
} else {
    sb <- readRDS(gns_bench_file_log_ubi)
}
```

>>>>

```{r, papa-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(otu_bench_file)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ibd_alm_results.tar.gz"
    saveRDS(sb, file = otu_bench_file)
} else {
    sb <- readRDS(otu_bench_file)
}
```

@@

```{r, papa-genus-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ibd_alm_results.tar.gz"
    saveRDS(sb, file = gns_bench_file)
} else {
    sb <- readRDS(gns_bench_file)
}
```

@@

```{r, papa-genus-logubi-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file_log_ubi)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ibd_alm_results.tar.gz"
    saveRDS(sb, file = gns_bench_file_log_ubi)
} else {
    sb <- readRDS(gns_bench_file_log_ubi)
}
```

### 2018-04-23 datasets/microbiome/microbiome-schubert.Rmd
Remove nmids and change ashs to ashq

```{r, schubert-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(otu_bench_file)) {
    nmids <- 150
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/cdi_schubert_results.tar.gz"
    saveRDS(sb, file = otu_bench_file)
} else {
    sb <- readRDS(otu_bench_file)
}
```

>>>>

```{r, schubert-sb, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(otu_bench_file)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/cdi_schubert_results.tar.gz"
    saveRDS(sb, file = otu_bench_file)
} else {
    sb <- readRDS(otu_bench_file)
}
```
